INSERT_TITLE_HERE

### 2020-10-26 manuscript.Rmd
added equation

There was a relatively small amount of missing data for most variables. However, given the data were longitudinal and included both linked administrative records and data collected from both the child's teacher and parent, missing data was inevitable. Attrition was offset by using applying combined sample and attrition weights constructed for the age 8 sample. Remaining missing data was small with the largest missing data proportion for teacher reported social skills at 14%. All other variables had 6% missing data or less (see code book in supplementary materials <!--# COnvert to OSF link when ready -->). To account for this, we constructed five imputed datasets using a bootstrapped expectation maximization procedure from the Amelia II package [@honaker2011]. These imputations were used in all analyses. All analyses were done using Bayes via the BRMS package in R [@bürkner2017]. The Bayes models were run once for each imputation and then the resulting posterior samples were pooled before point and uncertainty estimates were extracted. Interactions and their associated uncertainties were plotted by taking marginal effect estimates from a random 500 posterior draws for disadvantages (two standard deviations below the mean of SES), average, and advantaged (two standard deviations above the mean of SES) students [@gelman2020regression].

@@

>>>>

There was a relatively small amount of missing data for most variables. However, given the data were longitudinal and included both linked administrative records and data collected from both the child's teacher and parent, missing data was inevitable. Attrition was offset by using applying combined sample and attrition weights constructed for the age 8 sample. Remaining missing data was small with the largest missing data proportion for teacher reported social skills at 14%. All other variables had 6% missing data or less (see code book in supplementary materials <!--# Convert to OSF link when ready -->). To account for this, we constructed five imputed datasets using a bootstrapped expectation maximization procedure from the Amelia II package [@honaker2011]. These imputations were used in all analyses. All analyses were done using Bayes via the BRMS package in R [@bürkner2017]. The Bayes models were run once for each imputation and then the resulting posterior samples were pooled before point and uncertainty estimates were extracted. Interactions and their associated uncertainties were plotted by taking marginal effect estimates from a random 500 posterior draws for disadvantages (two standard deviations below the mean of SES), average, and advantaged (two standard deviations above the mean of SES) students [@gelman2020regression].

@@

The models are fit using the following formula:

$$
y^{*}_{i} \sim N(\alpha_{j[i]} + X_i\beta + \sigma^{2}_{y}), for~i = 1,...,n\\
\alpha_{j} \sim N(U_j \gamma, \sigma^{2}_{\alpha}), for~j = 1,...k
$$

Here $X_i$ is a matrix of individual level predictors including individual SES, prior social skills, gender, cohort, geographic location, and an NAPLAN achievement index. $U_j$ is a matrix of school level predictors including school section and the critical variable school SES. Note that we predict $y^{*}_{i}$ which is the latent continuous variable underlying the observed variables which is defined as:

$$
y_i =  \begin{cases}      y*_{i} & \text{if $y*_{i} < 0$ or $y*_{i} > 10 $}\\      0 & \text{if $y*_{i} < 0$}\\      10 & \text{if $y*_{i} > 10$}    \end{cases}
$$
